Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-10 csf-2017/paper.tex
Shrink figure a bit.

\begin{figure}
  \begin{tikzpicture}
    \draw[fill=gray!20,draw=none] (0,4) rectangle (4,3.5);
    \draw[fill=gray!20,draw=none] (0,0.5) rectangle (4,1);
    \draw (0,0.5) -- (0,4);
    \draw (4,0.5) -- (4,4);
    \draw (0,3.5) rectangle (4,3) node[pos=.5] {\footnotesize previous program counter};
    \draw (0,3) rectangle (4,2.5) node[pos=.5] {\footnotesize previous stack pointer};
    \draw (0,2.5) rectangle (4,1) node[pos=.5] {\footnotesize restore instructions};
    \draw (-2,2.25) node (rp) {return pointer};
    \draw[->] (rp.east) -- (-.2,2.25);
  \end{tikzpicture}

>>>>

\begin{figure}
  \begin{tikzpicture}[scale=.7, every node={scale=.7}]
    \draw[fill=gray!20,draw=none] (0,4) rectangle (6,3.5);
    \draw[fill=gray!20,draw=none] (0,0.5) rectangle (6,1);
    \draw (0,0.5) -- (0,4);
    \draw (6,0.5) -- (6,4);
    \draw (0,3.5) rectangle (6,3) node[pos=.5] {\footnotesize previous program counter};
    \draw (0,3) rectangle (6,2.5) node[pos=.5] {\footnotesize previous stack pointer};
    \draw (0,2.5) rectangle (6,1) node[pos=.5] {\footnotesize restore instructions};
    \draw (-3,2.25) node (rp) {return pointer};
    \draw[->] (rp.east) -- (-.2,2.25);
  \end{tikzpicture}
